Title

### 2021-04-11 submissiondraftNR.Rmd
final

The anxiety survey data posed a few difficulties.  First, the survey "weeks" were at irregular intervals and an inconsistent number of days.  The irregularity of the intervals can be seen by some gaps in observations in Figure \@ref{fig:usanx}.  Second, the survey method used the Census Bureau's Master Address File to send emails and texts to very large samples.  This method had high non-response rates and is likely subject to considerable bias, although this is a common feature of any survey data.  Third, the age ranges recorded in this survey begin with "18-29".  To demonstrate that this age range is highly relevant to university administration, data was obtained from the National Center for Education Statistics. Figure \@ref(fig:univpop) shows that ~30\% of 18-29 year-olds in the United States are in higher education and that of those in higher education in the US, ~75\% are between the ages 18 and 29.  Thus the mental health characteristics of the age bracket 18-29 are will apply to the vast majority of university students.

@@

As described in the technical documentation (LINK), the weeks of the Household Pulse Survey do not represent strict intervals of 7 days. For example, "Week 1" refers to data that was collected between April 23rd and May 5th, 2020, (13 days), but Week 9 refers to data that was collected between June 25th and June 30th, 2020 (6 days). The time points $s_i$ will be defined as the end date of each Week collection.

@@

This model allows for state-specific intercepts ($\alpha_s$), autocorrelation in anxiety within a state ($\beta_1$), and an effect of COVID cases on anxiety ($\beta_1$).

@@

We can see that both the lagged anxiety variable and LogCasesRatio are significant predictors. The value of the coefficient with $\mbox{COVID}_{s,t}$ shows that if new cases were to double from one week to the next, we expect our response anxiety odds to increase by `r round(fit.states.fixed$coefficients[1] * log(2), digits=4)`.

>>>>

The anxiety survey data posed a few difficulties.  First, the survey "weeks" were at irregular intervals and an inconsistent number of days.  The irregularity of the intervals can be seen by some gaps in observations in Figure \@ref{fig:usanx}.  Second, the survey method used the Census Bureau's Master Address File to send emails and texts to very large samples.  This method had high non-response rates and is likely subject to considerable bias, although this is a common feature of any survey data.  Third, the age ranges recorded in this survey begin with "18-29".  To demonstrate that this age range is highly relevant to university administration, data was obtained from the National Center for Education Statistics. Figure \@ref(fig:univpop) shows that ~30\% of 18-29 year-olds in the United States are in higher education and that of those in higher education in the US, ~75\% are between the ages 18 and 29.  Thus the mental health characteristics of the age bracket 18-29 will apply to the vast majority of university students.

@@

As described in the technical documentation, the weeks of the Household Pulse Survey do not represent strict intervals of 7 days. For example, "Week 1" refers to data that was collected between April 23rd and May 5th, 2020, (13 days), but Week 9 refers to data that was collected between June 25th and June 30th, 2020 (6 days). The time points $s_i$ will be defined as the end date of each Week collection.

@@

This model allows for state-specific intercepts ($\alpha_s$), autocorrelation in anxiety within a state ($\beta_1$), and an effect of COVID cases on anxiety ($\beta_2$).

@@

We can see that both the lagged anxiety variable and LogCasesRatio are significant predictors. The value of the coefficient with $\mbox{COVID}_{s,t}$ shows that if new cases were to double from one week to the next, we expect our response anxiety ratio to increase by `r round(fit.states.fixed$coefficients[1] * log(2), digits=4)`.
